---
title: "Final Project"
output: html_notebook
---
```{r}
#Installing the packages 
install.packages("stringr")
install.packages("caTools")
install.packages("gmodels")
install.packages("corrplot")
install.packages("Metrics")
install.packages("olsrr")
```

# Document Preparation
# Load libraries
```{r}
# Libraries
library(stringr)
library(tidyverse)
library(lubridate)
library(caTools)
library(class)
library(gmodels)
library(corrplot)
library(Metrics)
library(olsrr)
```
#Data Source: Google Data Studio

#This data is a csv exported from an seo agency's Google Organic Search data. There's 1,000 rows of information on specific keywords, categories, clicks, impressions, click through rates, and conversions. 

#The problem: Can we  predict the click through rate from a user on a given keyword or keyword intent?

#Intent for the purpose of this research will be classified in "Low" "Mid" and "High"

```{r}
agency <- read.csv("agency.csv", stringsAsFactors = T)

str(agency)
```
#Exploring the data

```{r}
summary(agency)
head(agency)
view(agency)
```
##We can see this data set has the following columns: 
#Keywords: the keywords or keyphrases users found to get to the agency's website.
#Category: the category of the topic of the keyword, if it's either about SEO, SaaS, Marketing, Link Building, if it's a Landing Page or other if it falls in another category. 
#Clicks: clicks made to the page form the given keyword.
#Impressions: impressions to the page from a given keyword. 
#CTR: % of users that clicked through the page after an impression.
#Position: the position of the page for a given keyword in Google's result page. 
#Conversions: number of conversions for a given keyword. 


# Data Transformation 

```{r}
# Adding a new column IF there's phrases within specific keywords using STR detect

#Using str I'm splitting the data in 3 different data sets filtering by the words that are associated to each intent

#In this case, according to the industry's standard the keywords best|agency|tools|consultant|consultancy are associated to High intent. 

#High Intent 
highintentstr <- agency %>% filter(str_detect(Keyword,("best|agency|tools|consultant|consultancy")))   
highintentstr
highintent <- highintentstr %>% mutate(intent = "High")
highintent

#Mid Intent 
midintentstr <- agency %>% filter(str_detect(Keyword,("how|what|who|when|where|why|which")))
midintent <- midintentstr %>% mutate(intent = "Mid")
midintent

#All the other intents are considered low 
lowintentstr <- agency %>% filter(!str_detect(Keyword,("best|agency|tools|consultant|consultancy|how|what|who|when|where|why|which")))
lowintent <- lowintentstr %>% mutate(intent = "Low")
lowintent

#Rbind all of them together
AgencyIntents<- rbind(highintent, midintent, lowintent)
View(AgencyIntents)
```

#We now created a new column with the intents for all keywords from industry standards. I did not use ifelse here because I couldn't find a way to include some phrases, so I did str and rbind instead. 

#Visualization 

```{r}
#Position and CTR for each Intent
ggplot(data = AgencyIntents, mapping = aes(x = Position, y = CTR, color = intent)) + geom_smooth()
```

```{r}
#Position and Clicks for each Intent
ggplot(data = AgencyIntents, mapping = aes(x = Position, y = Clicks, color = intent)) + geom_smooth()
```
```{r}
#Position and Clicks for each Category
ggplot(data = AgencyIntents, mapping = aes(x = Position, y = Clicks, color = Category)) + geom_point()
```

```{r}
#Position and Clicks for each Intent
ggplot(data = AgencyIntents, mapping = aes(x = Position, y = Clicks, color = intent)) + geom_point(aes(color = intent),size = 3,alpha = 0.8)
```
```{r}
#CTR and Clicks for each Intent
ggplot(data = AgencyIntents, mapping = aes(x = CTR, y = Clicks, color = intent)) + geom_point(aes(color = intent, size = 1))
```

```{r}
#CTR and Position for each Intent
ggplot(data = AgencyIntents, mapping = aes(x = CTR, y = Position)) + geom_point(aes(color = Category, size = .5))
```

```{r}
#Count per each Category
ggplot(AgencyIntents, aes(Category)) + geom_bar(aes(fill=Category))

#We can see here, the Category with the most keywords is Marketing 
```
```{r}
#Count for each Intent
ggplot(AgencyIntents, aes(intent)) + geom_bar(aes(fill=intent))

#The intent with the most keywords is "Low"
```
```{r}

```{r}
#Conversions per Intent 
ggplot(AgencyIntents, aes(x=intent, y=Conversions)) + 
  geom_bar(stat="identity", width=.5, fill = "blue") + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6))

#The sum of all low intent keywords have the most conversions
```
```{r}
#CTR per Intent 
ggplot(AgencyIntents, aes(x=intent, y=CTR)) + 
  geom_bar(stat="identity", width=.5, fill = "green") + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6))

#The sum of all low intent keywords have the biggest CTR
```
```{r}
 # Histogram on a Categorical variable
ggplot(AgencyIntents, aes(Category)) + geom_bar(aes(fill=intent), width = 0.5) + 
  theme(axis.text.x = element_text(angle=65, vjust=0.6)) + 
  labs(title="Histogram on Keyword Category", 
       subtitle="Intent per Keyword Category") 

#The keyword category with the higher intent is SEO
```

```{r}
ggplot(AgencyIntents, aes(Position))+ geom_density(aes(fill=factor(Category)), alpha=1) + 
    labs(title="Density plot", 
         caption="Source: agency",
         x="Position",
         fill="#Category")

#We can see here most Marketing keywords rank between 0-20
#SEO Keywords Rank from 0 to 120

```

```{r}
ggplot(AgencyIntents, aes(x = "", y=Conversions, fill = factor(Category))) + 
  geom_bar(width = 1, stat = "identity") +
  theme(axis.line = element_blank(), 
        plot.title = element_text(hjust=0.5)) + coord_polar(theta = "y", start=0)

#We can see the Marketing category is taking most of the visualizations
```

       
```{r}
#Sample Split

set.seed(123)

AgencyIntents$sample <- sample.split(AgencyIntents$intent, SplitRatio = 0.60)

train <- subset(AgencyIntents, sample == TRUE)

test <- subset(AgencyIntents, sample == FALSE)

str(AgencyIntents)
```
#Removing Non-Numeric elements

```{r}
view(AgencyIntents)
AgencyNumeric <- select(AgencyIntents,Clicks, Impressions, CTR, Position,Conversions )

droplevels(AgencyNumeric)
```


#Correlation Check

```{r}
AgencyCor<- cor(AgencyNumeric)
corrplot(AgencyCor, method = "number")
```
#Non Numeric Visualizations 
```{r}
#Impressions vs CTR
ggplot(data = AgencyNumeric, mapping = aes(x = CTR, y = Impressions, color = Clicks)) + geom_line()
```

```{r}
#CTR vs Position 
ggplot(data = AgencyNumeric, mapping = aes(x = Position, y = CTR)) + geom_line()
```
#First Model: Linear Regression and Stepwise

#Linear Regression
```{r}
AgencyModel <-  lm(CTR ~ Clicks + Impressions + Position + Conversions , data = AgencyNumeric)

AgencyPrediction <- predict(AgencyModel, test)

cat("Linear Regression RMSE:", rmse(AgencyPrediction, test$CTR), "\n")
```

#Stepwise
```{r}
#Forward
StepwiseForward <- ols_step_forward_p(AgencyModel, details = TRUE)
StepwiseForwardModelPrediction <- predict(StepwiseForward$model, test)
cat("Stepwise Forward RMSE:", rmse(StepwiseBackwardModelPrediction, test$CTR))

#Backward
StepwiseBackward <- ols_step_backward_p(AgencyModel, details = TRUE)
StepwiseBackwardModelPrediction <- predict(StepwiseBackward$model, test)
cat("Stepwise Backward RMSE:", rmse(StepwiseBackwardModelPrediction, test$CTR))

#Both 
StepwiseBoth <- ols_step_both_p(AgencyModel, details = TRUE)
StepwiseBothModelPrediction <- predict(StepwiseBoth$model, test)

cat("Stepwise Both RMSE:", rmse(StepwiseBothModelPrediction, test$CTR), "\n")

```
## In this case, all errors are the same.  
#Linear Regression RMSE: 6.311982 
#Stepwise Backward RMSE: 6.311982
#Stepwise Forward RMSE: 6.311982
#Stepwise Both RMSE: 6.311982 

# Second Model: KNN
#From the variables chosen by the on the regression method, I will create a K Nearest Neighbors model using the variables with the highest correlation and display the accurracy

#Although from part one, all Stepwise models output the same RMSE, I am using Stepwise Forward as it contains the least amount of variables.

#Stepwise Forward

#Variables Selected:CTR ~ Clicks + Impressions + Position + Conversions 
#From the Corelation Check, I'm choosing Clicks and Conversions since they are highly and positively correlated

```{r}

#CLicks and Conversions 
AgencyTrain <- select(train, Clicks, Conversions)

AgencyTest <- select(test, Clicks, Conversions)

PredictedClass <- knn(train = AgencyTrain, test = AgencyTest,cl = train$intent, k = 3)

AgencyConfusion <- table(PredictedClass, test$intent)

AccurracyAgency <- sum(diag(AgencyConfusion)) / sum(AgencyConfusion)


cat("Accurracy KNN:", AccurracyAgency)
```
```{r}
#Plotting Clicks and Conversions
```

```{r}
ggplot(data = AgencyIntents, mapping = aes (x = Clicks, y = Conversions, color = intent))+ geom_point()
```

```{r}
ggplot(data = AgencyIntents, mapping = aes (x = Clicks, y = Conversions, color = intent))+ geom_point() 
```



```{r}
#Position  and CTR 
AgencyTrain2 <- select(train, CTR, Position)

AgencyTest2 <- select(test, CTR, Position)

PredictedClass2 <- knn(train = AgencyTrain2, test = AgencyTest2,cl = train$intent, k = 3)

AgencyConfusion2 <- table(PredictedClass2, test$intent)

AccurracyAgency2 <- sum(diag(AgencyConfusion2)) / sum(AgencyConfusion2)


cat("Accurracy KNN:", AccurracyAgency2)
```

```{r}
ggplot(data = AgencyIntents, mapping = aes (x = CTR, y = Position, color = intent))+ geom_point() 
```

```{r}
#Conversions and Position 
AgencyTrain3 <- select(train, Conversions, Position)

AgencyTest3 <- select(test, Conversions, Position)

PredictedClass3 <- knn(train = AgencyTrain3, test = AgencyTest3,cl = train$intent, k = 3)

AgencyConfusion3 <- table(PredictedClass3, test$intent)

AccurracyAgency3 <- sum(diag(AgencyConfusion3)) / sum(AgencyConfusion3)


cat("Accurracy KNN:", AccurracyAgency3)
```

```{r}
ggplot(data = AgencyIntents, mapping = aes (x = Conversions, y = Position, color = intent))+ geom_point() 
```


```{r}
#Impressions and Clicks 
AgencyTrain4 <- select(train, Impressions, Clicks)

AgencyTest4 <- select(test, Impressions, Clicks)

PredictedClass4 <- knn(train = AgencyTrain4, test = AgencyTest4,cl = train$intent, k = 3)

AgencyConfusion4 <- table(PredictedClass4, test$intent)

AccurracyAgency4 <- sum(diag(AgencyConfusion4)) / sum(AgencyConfusion4)


cat("Accurracy KNN:", AccurracyAgency4)
```

```{r}
ggplot(data = AgencyIntents, mapping = aes (x = Impressions, y = Clicks, color = intent))+ geom_point() 
```


```{r}
#Create a new dataframe to store the accuracies of both models. 

df <- data.frame(Variable1 = c("Clicks","Conversions"),
                 Variable2 = c("Position", "CTR"),
                 Variable3 = c("Conversions","Position"),
                 Variable4 = c("Impressions", "Clicks"),
  accurracy = c(AccurracyAgency, AccurracyAgency2,AccurracyAgency3,AccurracyAgency4))
df
```
